Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2014-11-07 draft_lm1.tex
fixed stochastic model

In monitoring of infectious diseases, it is important to assess whether the 
incidence of a a particular disease is increasing significantly, in order to 
decide to take preventive measures.
The effective reproductive number at time $t$, \rr, can be understood as a 
real-time estimate of the basic reproductive number ($R_{0}$) and is defined as 
the average number of secondary cases per primary case at time $t$.
Here we derive confidence/credibility bounds for the uncertainty about the 
estimate of the effective reproductive number $R_t$ under the assumption that 
reported disease counts are Poisson distributed.
It is shown that one can construct a conservative confidence interval for \rr 
using the induced probability distribution that results from the approach of 
\cite{mantel}.

>>>>

In monitoring of infectious diseases, it is important to assess whether the 
incidence of a  particular disease is increasing significantly, in order to 
decide to take preventive measures.
The effective reproductive number at time $t$, \rr, can be understood as a 
real-time estimate of the basic reproductive number ($R_{0}$) and is defined as 
the average number of secondary cases per primary case at time $t$.
Here we derive confidence/credibility bounds for the uncertainty about the 
estimate of the effective reproductive number $R_t$ under the assumption that 
reported disease counts are Poisson distributed.
It is shown that one can construct a conservative confidence interval for \rr 
using the induced probability distribution that results from the approach of 
\cite{mantel}.
